NLIZE: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-23 paper/background.tex
update background
update paper structure
add figure for end2end
update intro

\section{Background}
\label{sec:languageInference}

@@

\subsection{Neural Network Primer}
\shusen{What is the basic understanding of neural network What is the end-to-end}

\subsection{Neural Network Model in NLP}
% \subsection{Interprebilty Challenges}
Compared with Conputer Vision, the discrete nature of words and sentences
presents additional challenge for
interpreting the model, since many visualization technique often employed
for images rely on continuous nature of the input space (e.g., one can interpolate
real values much easier than interplolate between words/sentences).
%
On the other hand, a majority of recent NLP neural networks share the nature of
end-to-end model, where the entire model operates as a black-box that takes
vectorized input and yields final prediction for a specific task.
Therefore, to study the inside of end-to-end neural models, it is important to
explore the interaction between intermediate representations and predictions.

The introduction of attention mechanism~\cite{bahdanau2014neural} allows
pairwise interaction between hidden states. This interaction can be naturally explained
as a form of alignment which exposes an interpretable layer in end-to-end neural networks.
Recently attention has contributed to many strongly-performed NLP models
~\cite{parikh2016emnlp},~\cite{rush2015neural},~\cite{yang2016hierarchical},
~\cite{seo2016bidirectional},~\cite{schwartz2017high}.
We will focus on its application in Natural Language Inference task as proposed in~\cite{parikh2016emnlp}.
However notice that our visualization can be generalized to other attention models as well.

\subsection{Natural Language Inference}
Natural Language Inference(cite?) is an important machine understanding task in NLP.
The problem definition is to classify the relationship between a premise sentence and a hypothesis sentence.
The prediction must fall in one of three catergories: $\{Entailment, Contradiction, Neutral\}$.
$Entailment$ refers to that the textual information of hypothesis is embedded in premise;
$Contradiction$ means the textuals of hypothesis opposes that of premise;
and $Neutral$ implies no conclusion can be made on either $Entailment$ or $Contradiction$.

>>>>

\section{Background}

@@

% \subsection{Neural Network Primer}

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{end2end}
 \caption{End-to-end attention based model.}
\label{fig:modelPipeline}
\end{figure}

\subsection{Neural Network Model in NLP}

\shusen{neural linguistic models?}

\shusen{What is the basic understanding of neural network What is the end-to-end}

% \subsection{Interprebilty Challenges}
Compared with Conputer Vision, the discrete nature of words and sentences
presents additional challenge for
interpreting the model, since many visualization technique often employed
for images rely on continuous nature of the input space (e.g., one can interpolate
real values much easier than interplolate between words/sentences).
%
On the other hand, a majority of recent NLP neural networks share the nature of
end-to-end model, where the entire model operates as a black-box that takes
vectorized input and yields final prediction for a specific task.
Therefore, to study the inside of end-to-end neural models, it is important to
explore the interaction between intermediate representations and predictions.

\subsection{Attention Mechansim}
\label{sec:attention}
The introduction of attention mechanism~\cite{bahdanau2014neural} allows
pairwise interaction between hidden states. This interaction can be naturally explained
as a form of alignment which exposes an interpretable layer in end-to-end neural networks.
Recently attention has contributed to many strongly-performed NLP models
~\cite{parikh2016emnlp},~\cite{rush2015neural},~\cite{yang2016hierarchical},
~\cite{seo2016bidirectional},~\cite{schwartz2017high}.
We will focus on its application in Natural Language Inference task as proposed in~\cite{parikh2016emnlp}.
However notice that our visualization can be generalized to other attention models as well.

\subsection{Natural Language Inference}
\label{sec:languageInference}
Natural Language Inference(cite?) is an important machine understanding task in NLP.
The problem definition is to classify the relationship between a premise sentence and a hypothesis sentence.
The prediction must fall in one of three catergories: $\{Entailment, Contradiction, Neutral\}$.
$Entailment$ refers to that the textual information of hypothesis is embedded in premise;
$Contradiction$ means the textuals of hypothesis opposes that of premise;
and $Neutral$ implies no conclusion can be made on either $Entailment$ or $Contradiction$.

### 2018-03-23 paper/task.tex
update intro

\section{Task Analysis}
\label{sec:task}
Effective identify and itemize the visualization tasks and the corresponding goal is the first step in designing a useful visual representation.

>>>>

\section{Task Analysis}
\label{sec:task}
Identify the analysis goals and distill the corresponding visualization tasks is the first yet significant step in designing a useful tool. In this section, we examine how domain experts approach the challenge of analyzing a new model and assess its strength and weakness.
Then, we reify the observations into a common paradigm and identify where and how a visualization tool could help experts interpret the model and development intuitive, more importantly, how the proposed fit into the domain experts' though process and workflow.

During our long-term collaboration with two domain experts in NLP, we have conducted extensive interview and discussion on the common approach researchers employ to interpret the behavior and obtain intuition for a new model.
%
Often, the most important metric for evaluating a model is the prediction accuracy. However, most researchers would agree, the accuracy alone does not provide the full picture. The model could perform much worse on a different test set. The model may produce many correct predictions for the ``wrong'' reasons (e.g., pickup unintended pattern in the training data that does not exist in real word scenarios).
%
As a result, NLP researchers often employ a set of tests, which are driven by their domain knowledge and hypotheses based on the architecture, to assess the model.
%
A stereotypical scenario can be summarized as the follow.
%
To assess a model for a specific NLP task, the research start the analysis by looking at the failure cases.

\shusen{What is the paradigm?}
Look at example, perturb the example, see how the perturb the one fails,

learn the limitation and strength from the where and how the errors occurs. iterate

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{errorAnalysis}
 \caption{How domain experts carry out error analysis on the model.}
\label{fig:modelPipeline}
\end{figure}
